Cryptanalysis of SBC based post-quantum signature scheme

### 2025-05-30 rapport.tex
petite remarque

% !TXS template
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[backend=bibtex]{biblatex}
\usepackage{csquotes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{stmaryrd}

@@

>>>>

% !TeX spellcheck = <none>
% !TXS template
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[backend=bibtex]{biblatex}
\usepackage{csquotes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{stmaryrd}

@@

		These are theoretical estimations and in practice it can be much more. For example, to represent a 67 bit number using the bignum implementation in the GMP library, we would need at least 32 bytes instead of the 9 that we estimated because of memory alignement and the total coast of the structure, but this can be optimized to use less memory for an array usage.

		\subsubsection{Space complexity of other attacks}
